Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-31 paper.qmd
chore: add new section on nix containers
chore: add rix and rixpress citations; start docker-nix combo

This paper focuses on two critical but often overlooked aspects of
reproducibility: *computational environment management* and *workflow
orchestration*. We present a comprehensive framework addressing both challenges
using the [Nix]{.pkg} package manager [@dolstra2004nix], making it accessible to
researchers through two [R]{.proglang} packages: [rix]{.pkg} and
[rixpress]{.pkg}. Before introducing these packages, we survey existing tools
and their limitations to contextualise our contributions.

@@

>>>>

This paper focuses on two critical but often overlooked aspects of
reproducibility: *computational environment management* and *workflow
orchestration*. We present a comprehensive framework addressing both challenges
using the [Nix]{.pkg} package manager [@dolstra2004nix], making it accessible to
researchers through two [R]{.proglang} packages: [rix]{.pkg} [@R-rix] and
[rixpress]{.pkg} [@R-rixpress]. Before introducing these packages, we survey
existing tools and their limitations to contextualise our contributions.

@@

Provisioning [Nix]{.pkg} in container images lowers the burden to install it on
the operating system of the host.
